\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=25mm,
 right=25mm,
 top=25mm,
 bottom=25mm
 }
\usepackage{url}
 
\usepackage{tikz}
\usetikzlibrary{automata,positioning}

\input{macro}


\title{CSE332 Theory of Computation \\ Homework 1}
\author{Instructor: Mijung Kim}
\date{Due: Tuesday, October 11, 2022 at 11:59pm on Blackboard}

\begin{document}

\maketitle

\section*{General Information}
This homework is worth 10\% of your final grade. It has 10 problems worth 130 points in total.

\noindent We take cheating very  seriously. Please revisit and be well-noted with Syllabus and CSE Cheating Policy on Blackboard. 

\noindent If you have any questions, please actively use Pizza at \url{http://piazza.com/unist.ac.kr/fall2022/cse332} or TA's Office Hours.


\section*{Submission Guidelines} 

Your homework must be typed in \texttt{LaTeX} and compiled into a PDF. This PDF file should be submitted on Blackboard. Please note that \textbf{no late submission will be accepted}.

\section*{\texttt{LaTeX} Guidelines}

We recommend to use \texttt{Overleaf} for editing and compiling your \texttt{.tex} files. For a reference, we provided the original \texttt{tex} files that we used to write this homework. Those files are included in the attached \texttt{hw.zip} file.  At \url{overleaf.com},  go to \texttt{New Project} $>$ \texttt{Upload Project} and upload the attached zip file. In the created project, you can get the PDF file by compiling \texttt{hw1.tex}. If you have difficulties in using  \texttt{LaTeX}, please ask TAs for help on Piazza or during their Office Hours. 

\section*{Problems} 

\noindent \textbf{Problem 1} (10pts) Prove that $(uv)^{R} = v^{R}u^{R}$ for all $u,v \in \Alphabet^{+}$. (Hint: Use induction on the length of $v$.) \\

    
\noindent \textbf{Problem 2} (10pts) Consider the following language: $L = \{w\in\{0,1\}^{*} \, | \, w$  ends with 1001.$\}$.
    \begin{enumerate}
        \item (5pts) Design a DFA that accepts $L$.
        \item (5pts) Design an NFA that accepts $L$.
    \end{enumerate}
    
\noindent \textbf{Problem 3} (10pts) Design an NFA to recognize the strings that represent real numbers. Assume $\Alphabet = \{0,1,2,3,4,5,6,7,8,9,.\}$. For example, the NFA should accept strings such as ``1.0", ``12.156", and ``.01", but must reject strings such as ``0.5.1", ``12.", and ``3".

\noindent \newline \textbf{Problem 4} (20pts) Use subset construction to convert the following NFA to a DFA:
\begin{center}
    \begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,auto] 
        \node[state,initial] (q_0)   {$q_0$}; 
        \node[state] (q_1) [right=of q_0] {$q_1$}; 
        \node[state] (q_2) [right=of q_1] {$q_2$};
        \node[state,accepting] (q_3) [right=of q_2] {$q_3$}; 
        \path[->]
        (q_0) edge node {$a$} (q_1)
        (q_1) edge node {$a,b$} (q_2)
        (q_2) edge node {$a$} (q_3)
        (q_0) edge [loop below] node {$a,b$} ()
        (q_3) edge [loop below] node {$a,b$} ();
    \end{tikzpicture}
\end{center}

\noindent \textbf{Problem 5} (10pts) Design an $\epsilon$-NFA that accepts the following language:
\begin{center}
    $L = \{a^{m}b^{n}c^{o}\,|\,m,n,o \geq 0\}$
\end{center}

\noindent \textbf{Problem 6} (20pts) Consider the following transition table of an $\epsilon$-NFA:
    \begin{center}
    \small
        \begin{tabular}{r||c|c|c|c}
        & $\epsilon$ & $a$ & $b$ & $c$\\ \hline\hline
        $p$ & $\emptyset$ & $\{p\}$ & $\{q\}$ & $\{r\}$\\ 
        $q$ & $\{p\}$ & $\{q\}$ & $\{r\}$ & $\emptyset$\\ 
        $r$ & $\{q\}$ & $\{r\}$ & $\emptyset$ & $\{p\}$\\ 
        \end{tabular}
    \end{center}
    where $p$ is the initial state and $r$ is the final state.
    \begin{enumerate}
        \item (10pts) Compute the $\epsilon$-closure(EClosure) of each state.
        \item (10pts) Convert the automaton to a DFA.
    \end{enumerate}
    
\noindent \textbf{Problem 7} (15pts, 5pts each) Find regular expressions for the following languages.
\begin{enumerate}
    \item $L = \myset{\omega \in \myset{a,b,c}^* \mid \omega \mbox{ has no more than three $a$'s}}$
    \item $L = \myset{\omega \in \myset{0,1}^* \mid \omega \mbox{ begins and ends with 0 and contains at least one 1}}$
    \item $L = \myset{\omega \in \myset{0,1}^* \mid \omega \mbox{ does not contain 111}}$ 
    % \item $S = \myset{2,4,6,\dots} = \myset{x \in \mbn \mid \mbox{$x$ is even}}$
\end{enumerate}

\noindent \textbf{Problem 8} (20pts) Consider a DFA represented by a transition table:
\begin{center}
\small
\begin{tabular}{r|c|c}
& 0 & 1 \\ \hline
$\rightarrow q_1$ & $q_2$ & $q_1$ \\ 
$q_2$ & $q_3$ & $q_1$ \\ 
$*q_3$ & $q_3$ & $q_2$
\end{tabular}
\end{center}
Give all the regular expressions $R^{(0)}_{ij}$,$R^{(1)}_{ij}$,$R^{(2)}_{ij}$. Try to simplify the expressions as much as possible.
Think of state $q_i$ as if it were the state with number $i$.

\noindent \newline \textbf{Problem 9} (10pts) Convert the following regular expressions to finite automata ($\epsilon$-NFA): $ab^*aa+bba^*ab$ \\

\noindent \textbf{Problem 10} (10pts) Find a $\epsilon$-NFA that accepts language $L(ab^*a^*)\cap L(a^*b^*a)$.


\end{document}

